\Title

### 2019-12-23 manuscript/manuscript.tex
Continue writing manuscript

Mathematical background of the EQL\@.
How it can be understood in terms of Green's functions problem.

@@

Describe the proposed source distributions as combination of layouts and depths
strategies.

@@

The \emph{regular grid} creates an homogeneous distribution of point sources bellow the
surveyed region.
It could create too many sources on areas without data and very few ones on
areas with a high number of observation points, leading to an underfitting of the
observed data.
This could be solved by reducing the grid spacing and therefore increasing the number of
point sources, heavily increasing the computational load of the interpolation process.

@@

@@

Describe the ground and airborne survey (plus noise).
Show survey values.

@@

Describe the target grid. Show target grid figure.
Describe the parameters used for each source distribution, how do we score each interpolation.
Describe the Harmonica implementation of the EQL.

Show results.

>>>>

Mathematical background of the EQL\@.
How it can be understood in terms of Green's functions problem.
EQL implementation on Harmonica.

@@

% Describe the proposed source distributions as combination of layouts and depths
% strategies.

@@

The \emph{regular grid} creates an homogeneous distribution of point sources bellow the
surveyed region.
It could create too many sources on areas without data and very few ones on
areas with a high number of observation points, leading to an underfitting of the
observed data.
This could be solved by reducing the grid spacing and therefore increasing the number of
point sources and the computational load of the interpolation process.

@@

Compare the accuracy of the predictions made by each source distribution.
Need an objective way to compare them.
Propose a synthetic gravity model made out of prisms of different sizes and density
contrasts.
Create a regular grid of observation points where the gravitational effect of the
synthetic model will be computed.
Call it the \emph{target grid}.
Generate synthetic surveys above the same synthetic model and compute the gravitational
effect of the model on each survey.
Use each source distribution to predict values based on the ones obtained on each survey
onto the same grid points of the \emph{target grid}.
Score each interpolation by comparing the predicted values with the \emph{target grid}.
Finally compare the accuracy of the predictions made by each source distribution.

@@

Create synthetic surveys to produce observation points.
In order to compare each source layout under very different set of observation points we
create a ground and an airborne synthetic surveys.
We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J. Kleywegt
et al.\ and made available through the NOAA website
(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating a synthetic
ground survey.
We selected a portion of the Great Britain Aeromagnetic Survey acquired by Hunting
Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955 and 1965 and made
available by the
\href{
    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
    }{
    British Geological Survey (BGS)
}, for creating a synthetic airborne survey.

The gravitation effect of the synthetic model has been computed on both surveys and
added Gaussian noise (standard deviation of 1mGal) to simulate acquisition errors.

@@

%Describe the target grid. Show target grid figure.
%Describe the parameters used for each source distribution, how do we score each interpolation.
%Describe the Harmonica implementation of the EQL.
%Show results.

Compute the gravitational effect of the synthetic model on a regular grid of points
located at the same height.
This will be called our \emph{target grid}.
We will use it to compute the accuracy of the predictions made by each source
distribution.

Take a source distribution, fit the source coefficients and then use them to predict
data on the grid points where the \emph{target grid} is defined.
Define prediction error as the difference between the predicted values and the
\emph{target grid}.

Each source distribution has parameters that need to be specified before fitting its
coefficients.
For example, the \emph{grid of sources} needs the depth at which the sources will be
located.
The damping parameter used on the fitting process must also be specified beforehand.
These parameters play an important role on the accuracy of the prediction.
We compute several predictions made by the same source distribution, but with different
values for its parameters.
Then we score each interpolation by computing the R$^2$ between each prediction and the
target grid.
We keep the best prediction, i.e.\ the one that has the highest R$^2$ score.
